
---
title: "0925 Data Review Zillow Competition"
output: html_notebook
---

```{r}
library(tianweiR)
library(dplyr)
library(ggplot2)
library(data.table)
library(caret)
```

# load data
```{r}
data_property=fread('Data/properties_2016.csv',na.strings = c('NA','na','',' '))
data_train=fread('Data/train_2016_v2.csv',na.strings = c('NA','na','',' '))
data_test=fread('Data/sample_submission.csv',header = T,na.strings = c('NA','na','',' '))
```

## link property to error file
```{r}
data_all=data_train%>%left_join(data_property)
```

```{r}
head(data_all)
```


```{r}
str(data_all)
```
## give NA 0 values
```{r}
data_all[is.na(data_all)]=0
```

## Correct data type
```{r}
factor_col_index=which(colnames(data_all) %like% 'id')
colnames(data_all)[factor_col_index]
for (i in factor_col_index){
  data_all[,i]=as.factor(data_all[,i])
}
```

Correct columns that are factors with no id in names

roomcnt missing?? why, probably cannot give it 0
```{r}
data_all$hashottuborspa=as.factor(data_all$hashottuborspa)
data_all$propertycountylandusecode=as.factor(data_all$propertycountylandusecode)
data_all$rawcensustractandblock=as.factor(data_all$rawcensustractandblock)
data_all$taxdelinquencyflag=as.factor(data_all$taxdelinquencyflag)
```




# Explorary Data Analysis

we have some records with multiple entries
```{r}
data_train%>%
  group_by(parcelid)%>%
  summarise(num_entry=length(unique(transactiondate)))%>%
  filter(num_entry>1)%>%
  arrange(-num_entry)
```


```{r}
data_1=data_train%>%filter(parcelid=='10821829')
```

### Check distribution of all numeric columns
```{r}
  num_col_index=seq(1:ncol(data_all))[sapply(data_all,is.numeric)]

  for(i in num_col_index){
    hist(data_all[,i],50,main = paste('Distribution of',colnames(data_all)[i]),xlab=colnames(data_all)[i])
  }
  
```

### continue to correct variables 
```{r}
summary(data_all$basementsqft)
```
looks like only 1 value existed
```{r}
data_all=data_all%>%
  select(
    -basementsqft,
    -finishedfloor1squarefeet,
    -finishedsquarefeet13,
    -finishedsquarefeet15,
    -finishedsquarefeet50,
    -finishedsquarefeet6,
    -lotsizesquarefeet,
    -poolsizesum,
    -unitcnt,
    -yardbuildingsqft17,
    -yardbuildingsqft26
    
  )
```


 
```{r}
str(data_all)
```

## correlation analysis
```{r}
plot(data_all$logerror,data_all$taxvaluedollarcnt)
```


# Prepare training data
```{r}
library(sqldf)
data_unique=sqldf('select a.*
from data_train a
inner join (select parcelid, min(date(transactiondate)) min_tran from data_train group by parcelid) b
on a.parcelid=b.parcelid and a.transactiondate=b.min_tran
      ',method = "raw")

nrow(data_unique)
```

```{r}
length(unique(data_train$parcelid))
```


```{r}
data_unique
```

## split data into internal train and test sets

Initial approach on missing value: set NA=-1
```{r}
data_unique[is.na(data_unique)]=-1
```

Create dummy variables
```{r}
data_transform=model.matrix(logerror~.-parcelid-transactiondate-1, data=data_unique)
data_transform=as.data.frame(data_transform)
data_transform$logerror=data_unique$logerror
```

```{r}
head(data_transform)
```



```{r}
train_index=createDataPartition(y = data_unique$logerror,p = 0.8)
data_train_internal=data_transform[train_index$Resample1,]
data_test_internal=data_transform[-train_index$Resample1,]
```

```{r}
train_y=data_train_internal$logerror
train_x=as.matrix(data_train_internal%>%select(-logerror))

test_y=data_test_internal$logerror
test_x=as.matrix(data_test_internal%>%select(-logerror))
```

```{r}
dim(train_x)
```

```{r}
hist(train_y,n=500)
```


# Experiment with Neural Network
```{r}
library(keras)
```

```{r}
model <- keras_model_sequential() 
model %>% 
  layer_dense(units = 10, activation = 'relu', input_shape = c(2129)) %>% 
  layer_dropout(rate = 0.5) %>%
  layer_dense(units = 10, activation = 'relu') %>%
  layer_dropout(rate = 0.5) %>%
  layer_dense(units = 1, activation = 'softmax')%>%
  compile(
  optimizer = optimizer_rmsprop(lr = 0.0001),
  loss = 'mse'
)
```

```{r}
model %>% fit(train_x, train_y, epochs=1)

```

```{r}
summary(model)
```

predict test data
```{r}
predicted_test=predict(model,test_x)

plot(predicted_test,test_y)
```

